Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-02-01 Documents/Talk/content.tex
StarField results
Working on the slides

@@

\begin{frame}[t]{View of data analysis}
All conclusions are probabilities.
\vspace{20pt}

@@

\begin{frame}[t]{Birth and Death}
For problems of unknown dimensionality, the hypothesis space is the union
of several fixed-dimension hypothesis spaces. Can add {\bf birth and death}
proposals that try to increase or decrease the number of objects in the model.

@@

\begin{frame}[t]{Results from the galaxy data}
\begin{center}
\includegraphics[scale=0.45]{../Paper/N_galaxy_result.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Galaxy data movie}
{\tt https://www.youtube.com/watch?v=s1udKctW2HY}
\end{frame}

\begin{frame}[t]{Exoplanets}
Radial velocity data is considered challenging
\end{frame}

>>>>

\begin{frame}[t]{Marginal Likelihood and Model Selection}
The marginal likelihood is more than a normalising constant. Consider
estimating parameters $\theta$ within a model $M$. The marginal likelihood
is really
\begin{equation}
p(D|M) = \int p(\theta | M)p(D|\theta, M) \, d\theta
\end{equation}
which can
be used as a likelihood if we want to calculate the plausibility of $M$ vs.
an alternative.
\end{frame}

@@

\begin{frame}[t]{View of data analysis}
All conclusions are probabilities, and probabilities are plausibilities.
\vspace{20pt}

@@

\begin{frame}[t]{Popular but slow approach}
The marginal posterior distribution for $N$ be written down directly
using Bayes' rule with $N$ as the only unknown parameter:
\begin{eqnarray}
p(N | D) &=& \frac{p(N)p(D | N)}{\sum_N p(N)p(D | N)}.
\end{eqnarray}
where
\begin{eqnarray}
p(D | N) &=& \int p(\theta | N) p(D | \theta, N) \, d^n \theta
\end{eqnarray}
\end{frame}

\begin{frame}[t]{Popular but slow approach}
Use many trial values of $N$ and use some Monte Carlo method to do the integral
for each $N$.
\end{frame}

\begin{frame}[t]{Alternative: Birth and Death}
For problems of unknown dimensionality, the hypothesis space is the union
of several fixed-dimension hypothesis spaces. Can add {\bf birth and death}
proposals that try to increase or decrease the number of objects in the model.

@@

\begin{frame}[t]{Probabilistic catalogs}
\begin{center}
\includegraphics[scale=0.25]{StarFieldFigures/catalogs.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Hyperparameters}
\begin{center}
\includegraphics[scale=0.3]{StarFieldFigures/inference2.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Luminosity Function}
\begin{center}
\includegraphics[scale=0.35]{StarFieldFigures/luminosity_function.pdf}
\end{center}
\end{frame}

\begin{frame}[t]{Exoplanets}
Radial velocity data is considered challenging. There are many systems where
controversy rages over $N$.
\end{frame}

\begin{frame}[t]{Exoplanets}
Radial velocity data is considered challenging. There are many systems where
controversy rages over $N$.
\end{frame}
